Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-10 chapters/final_remarks.tex
Changes 1. Revised conclusion and added aim 3 findings

In Aim 3 we investigate the rheological response of bijels stabilized with ellipsoidal particles under constant shear and show that the application of magnetic
fields changes the shear thinning properties of bijels.

@@

This work utilized 2 ellipsoidal particle geometries chosen for comparisons to previous literature using this 
particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
particle stabilized emulsions.These particles have also been shown to have capillary bridging and particle stacking,
not seen in the particles used in this work. These particles in bulk have been shown to have some intrinsic ordering
that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 
instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
\textcolor{blue}{https://doi.org/10.1039/D1SM00367D}

Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass 
transition points and rheological behavior from their hard sphere counterparts. In bijels, cohesive particles in 
particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, 
allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical engineering 
applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli 
response through temperature or pH. LBM methods that implement the immersed boundary method can be used to model soft
particles with a DLVO potential used to model electrostatics between particles. \textcolor{blue}{https://doi.org/10.1039/D3SM01648J}

>>>>

In Aim 3, we examine the rheological behavior of bijels stabilized by ellipsoidal particles under constant shear and demonstrate that the application of 
magnetic fields alters their shear-thinning properties and the yield stress of the bijel. This effect arises from variations in particle ordering at the interface, 
either due to the introduction of a magnetic field or pre-existing order in templated systems. Enhanced particle ordering facilitates smoother particle rearrangement, reducing local disruptions 
in the interfacial structure. The observed domain coarsening is primarily driven by shear-induced particle tilting or ejection from the interface, further 
influencing the overall microstructural evolution.

@@

This work utilized 2 ellipsoidal particle geometries chosen for comparisons to previous literature using this 
particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
particle stabilized emulsions.These particles have also been shown to have capillary bridging and particle stacking,
not seen in the particles used in this work. These particles in bulk have been shown to have some intrinsic ordering
that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 
instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
\cite{tan_2d_2021}

Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass 
transition points and rheological behavior from their hard sphere counterparts. In bijels, cohesive particles in 
particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, 
allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical engineering 
applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli 
response through temperature or pH. LBM methods that implement the immersed boundary method can be used to model soft
particles with a DLVO potential used to model electrostatics between particles. \cite{silva_lattice_2024}
